More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-10-04 2016-Weak-FH-Bisim/WeakBisim.tex
notations

Let $\uplus$ be the disjoint union operator on indexed sets. 
The elements
of the union are then accessed by using an index of one of the two
joined families.
We suppose here that disjoint unions are always well defined; this
requires to choose disjoint  
indices in the definition of the component system (e.g. name of
methods of different interfaces).
We denote $y\gets x$ a substitution. Application of the substitution is denoted
$\subst{y\gets x}$, the operation replaces in a term all occurrences 
of the term $y$ by the term $x$ (note that the absence of binders makes this operation 
trivial).

@@

\RAB{Exemple a revoir. Les regles ne passent...}

@@

Weak symbolic bisimulation was introduced to relate transition systems
that have indistinguishable behaviour, with respect to some definition
of \emph{internal actions} that are considered local to some
subsystem, and consequently cannot be observed, nor used for
synchronisation with their context.
As the notions of invisible action varies in different contexts,
e.g. $tau$ in CCS, and $i$ in Lotos, we will rely here on some set of
\emph{internal actions} depending on a specific action
algebra. Naturely, an internal action cannot be synchronised with
actions of other systems in its environment.

@@

Classicaly, we start by defining a derived transition relation based
on sequences of invisible actions:

@@

Two pNets are Weak FH-bisimilar if there exist a relation between their associated 
automata that is an Weak FH-bisimulation and their initial sstates are equivalent.

>>>>

Let $\uplus$ be the disjoint union operator on indexed sets. 
The elements
of the union are then accessed by using an index of one of the two
joined families.
We suppose here that disjoint unions are always well defined; this
requires to choose disjoint  
indices in the definition of the component system (e.g. name of
methods of different interfaces).
We denote $y\gets x$ a substitution. The application of the substitution is denoted
$\subst{y\gets x}$, the operation replaces in a term all occurrences 
of the term $y$ by the term $x$ (note that the absence of binders makes this operation 
trivial).

@@

\RAB{Exemple  Fig3 a revoir: Les regles ne passent... }

@@

Weak symbolic bisimulation was introduced to relate transition systems
that have indistinguishable behaviour, with respect to some definition
of \emph{internal actions} that are considered local to some
subsystem, and consequently cannot be observed, nor used for
synchronisation with their context.
As the notions of invisible action varies in different contexts,
e.g. $tau$ in CCS, and $i$ in Lotos, we will rely here on some set of
\emph{internal actions} depending on a specific action
algebra. Naturally, an internal action cannot be synchronised with
actions of other systems in its environment.

@@

Classically, we start by defining a derived transition relation based
on sequences of invisible actions:

@@

Two pNets are Weak FH-bisimilar if there exist a relation between their associated open
automata that is an Weak FH-bisimulation and their initial states are equivalent.
